### 2019-12-09 ch10_discussion/content.tex
update

In \textbf{Casewise NI}, one regulatory network is predicted for every single-cell in the dataset. Doing so allows studying the heterogeneity (or homogeneity) between and within different cell populations. In essence, most analyses that can be run on single-cell omics (e.g. diffential expression) can also be applied on casewise regulatory networks (e.g. to predict differentially expressed interactions).
It is the most generalised form of NI of the variants discussed above, as a casewise regulatory network can be clustered to create a differential network, or trajectory inference can be applied to derive a dynamic regulatory network. Examples of casewise NI methods include SCENIC \cite{aibar_scenicsinglecellregulatory_2017}, SSN \cite{liu_personalizedcharacterizationdiseases_2016}, and LIONESS \cite{kuijjer_estimatingsamplespecificregulatory_2019}.

Instead of inferring gene regulatory mechanisms occurring within a cell, \textbf{intercellular NI} methods study communication between cells by predicting interactions between the ligands of one type of cells and the receptors of another group of cells.

% browaeys_nichenetmodelinginterce

Hence, there is a need for compu-
tational methodologies that use expression data of interacting cells
to infer the effects of sender-cell ligands on receiver-cell expression.
Although a few basic methods were developed for bulk data (for
example, CCCExplorer) 15,16 , comprehensive and predictive methods
that are generally applicable to both bulk and single-cell expression
data are lacking.

% When does a cluster represent a new cell type? \cite{kiselev_challengesunsupervisedclustering_2019}

@@

Honourable mentions go to Linux, Fedora, \LaTeX, TeXstudio, (R)Markdown, Bash, Sed, Regular expressions, Rocket Chat, for making bioinformatics software development even more fun and enjoyable.

% ideas:
%  Yet I wonder how the current academic system
%can support such concepts. Academics often hold different positions in
%different research groups around the world, who should be the maintainer in
%these cases? The original PhD students that developed the work? The original
%research group?

%The eight chapter is a manuscript in preparation about the assessment of TI methods. The main discussion topic is the lack of a quantitative measure for the scoring of new TI methods. This leads to the publication and development of new methods that do not show a clear performance improvement compared to other methods. The main topic touches
%upon some sore points that are inherent in bioinformatics. The main thought I have with
%this chapter is that defining clear goals in an emerging technology is difficult and therefore is sometimes ignored by fellow bioinformaticians. This because the lack of standardized performance metrics, missing public datasets that are well described and an \textit{ad hoc} problem definition. I follow the idea of defining a clear cut approach to benchmarking (as described in chapter nine) and I like the proposition that is started in this manuscript for a discussion on good TI metrics.} Would approaches like e.g. DREAM challenges be a means of tackling these issues to your opinion?

% zie peter dawyndt, chapter 5
\clearpage
\section{References}
\printbibliography[heading=none]

>>>>

In \textbf{casewise NI}, one regulatory network is predicted for every single-cell in the dataset. Doing so allows studying the heterogeneity (or homogeneity) between and within different cell populations. In essence, most analyses that can be run on single-cell omics (e.g. diffential expression) can also be applied on casewise regulatory networks (e.g. to predict differentially expressed interactions).
It is the most generalised form of NI of the variants discussed above, as a casewise regulatory network can be clustered to create a differential network, or trajectory inference can be applied to derive a dynamic regulatory network. Examples of casewise NI methods include SCENIC \cite{aibar_scenicsinglecellregulatory_2017}, SSN \cite{liu_personalizedcharacterizationdiseases_2016}, and LIONESS \cite{kuijjer_estimatingsamplespecificregulatory_2019}.

Instead of inferring gene regulatory mechanisms occurring within a cell, \textbf{intercellular NI} methods \cite{efremova_cellphonedbv2inferring_2019,browaeys_nichenetmodelingintercellular_2019} study communication between cells by predicting interactions between the ligands of one type of cells and the receptors of another group of cells. Such methods typically require much more prior data (e.g. which cells are communicating with which cells, what are the ligands and receptors), but allows studying how the cells react to their environment and investigate intercellular feedback mechanisms.

@@

Honourable mentions are Linux, Fedora, \LaTeX, TeXstudio, (R)Markdown, Bash, Sed, Regular expressions, Rocket Chat, for making bioinformatics software development even more fun and enjoyable.

\clearpage
\section{References}
\printbibliography[heading=none]

### 2019-12-09 chX_backmatter.tex
update

I was told that the end of the dissertation is the right place to thank friends, family, and colleagues for their continued support during my PhD. Nobody ever specified \textit{which} end of the book. This is not the right end you're looking at.

Hello there! Did you stumble across this phrase by accident, 
or are you looking for what I think you're looking for?

>>>>

This dissertation would never have seen the light of day were it not for the continued support of many friends, family, and colleagues. While writing the dissertation, Caro told me that the right place to thank everybody was at the end of the book. It was not specified \textit{which} end of the book I should be using for this. This isn't the Acknowledgement section you're looking for.
